What do incoming university students believe about open science practices in

### 2021-04-19 analysis/Manuscript.Rmd

The most comprehensive set of principles for how science *ought* to be practiced are Merton's (1942) norms of science. Scientists (Anderson et al., 2000) and graduate students (Anderson & Louis, 1994) alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms. For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report. In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.

>>>>

The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942]. Scientists [@Anderson2000] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms. For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report. In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.<!--Should we consider citing someone for these links? Personally I have seen Simine draw these parallels between norms and open science practices and would favour crediting her here, however I'm sure that others have made similar analyses and so would be happy to cite others or to see this as such a commonly held set of beliefs that no citations are required--->
